\documentclass[a4paper,11pt,sans]{moderncv}

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%%% fontes %%%
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry} % Reduce document margins

\firstname{Plinio}
\familyname{Freire}
\title{Software Engineer}
\phone{+55 19 99839-5045}
\email{plinio.freire@gmail.com}

\nopagenumbers{}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle

%\section{\textsc{Informações Pessoais}}
%\cvitem{Nome}{Plinio Augusto Soriano Freire}
%\cvitem{Nascimento}{20 de abril de 1990}
%\cvitem{Cidade}{Campinas - SP}
%\cvitem{Nacionalidade}{Brasileira}
%\cvitem{Estado civil}{Solteiro}

\section{\textsc{Technical skills}}
\cvline{Infrastructure}{\small{AWS, Data centers, Networking, QEMU/KVM, Docker Containers}}
\cvline{OS}{\small{Any Linux distribution}}
\cvline{General tools}{\small{Tomcat, Apache, Nginx, Postfix, Cyrus IMAP, Mailman, ProFTP, NTP, DHCP, DNS, iptables, monit, nagios, ELK stack}}
\cvline{Programming}{\small{Bash, Python, PHP, Ruby, Java, Perl, C, Javascript}}
\cvline{Frameworks}{\small{Django, Rails, Pear, Jquery}}
\cvline{Database}{\small{MySQL, PostgreSQL}}
\cvline{SCM}{\small{Git}}
\cvline{Automation}{\small{Jenkins, Puppet, Gerrit, Robot Framework}}

\section{\textsc{Languages}}
\cvlanguage{English}{Fluent}{Full professional proficiency}
\cvlanguage{Portuguese}{Native}{Native proficiency}


\section{Experience}
\cventry{\scriptsize 01/2013 -- Current}{Software Developer | Software Engineer}{IBM}{}{}{
   The {\color{blue}\href{http://www-03.ibm.com/linux/ltc/index.html}{IBM Linux Technology Center}} is the IBM open source development branch.\newline
   Development and maintenance of code and applications.\newline
   Architecture and planning of new solutions and tools migration.\newline
   I have worked with the development of various types of programs (from web pages to linux kernel modules), application debugging, bugfixes as well as application performance improvement and parallel programing.\newline
}

\cventry{\scriptsize 08/2017 -- 09/2017}{Software Developer}{Husky}{}{}{
    Freelance work for {\color{blue}\href{https://husky.io/}{Husky}}.\newline
    The job was to develop a microservice to perform OCR in document images. I used Spring Boot, web sockets and Google Cloud Vision API.
}

\cventry{\scriptsize 2016 -- current}{Devops}{Freelancer}{}{}{
    As a LPI certified and a Linux expert I usually get freelance work as a devops and system administrator.\newline
    Tasks such as: web server configuring, automation of application deployment, Linux maintenance (updates and security fixes), configuration as code, Jenkins job creation and maintenance, system/application monitoring.
}

\cventry{\scriptsize 01/2012 -- 12/2012}{Intern}{IBM}{}{} {
    Development of a Software Development Kit based on Eclipse.
}

\section{Education}
\cventry{2008 -- 2012}{Bachelor of Science in Computer Engineering}{State University of Campinas (UNICAMP)}{Campinas - SP}{}{}

\section{Awards, Certifications and Associations}
\cvline{}{- 2016 Patent File Award}{}{}
\cvline{}{- 2015 Patent File Award}{}{}
\cvline{}{- 2014 IBM Manager’s Choice Award}{}{}
\cvline{}{- Linux Professional Institute Level 1 certified}{}{}
\cvline{}{- Novell Certified Linux Administrator}{}{}

\section{Publications}
\cvline{11/13/2015}{An Efficient Massive Deploy System on Cloud using a Distributed Protocol (http://priorart.ip.com/IPCOM/000244139D)}{}{}

\section{Patents}
\cvline{}{- Container VMzation based on monitoring rule, \textbf{status:} Filled}
\cvline{}{- Method for malware identification and efficient fix over a segregated domains in a cloud, \textbf{status:} Filled}

\end{document}
